---
title: "Conference Competitiveness"
---

::: {.hero-banner}
::: {.hero-content}
# Conference Competitiveness Analysis
Compare NAIA women's wrestling conferences by national tournament points, individual All-Americans, win percentages, and national champions.
:::
:::

::: {.stats-grid}
::: {.stat-card}
::: {.stat-number}
Mid-South
:::
::: {.stat-label}
#1 Most Competitive Conference
:::
:::

::: {.stat-card}
::: {.stat-number}
818 pts
:::
::: {.stat-label}
Mid-South Total Points
:::
:::

::: {.stat-card}
::: {.stat-number}
43
:::
::: {.stat-label}
Mid-South All-Americans
:::
:::

::: {.stat-card}
::: {.stat-number}
55.2%
:::
::: {.stat-label}
Highest Win Rate
:::
:::
:::

## Conference Performance Summary

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9
#| fig-height: 4.8

library(tidyverse)
library(htmltools)

conf_data <- read_csv("data/conference_comparison.csv", show_col_types = FALSE)

ggplot(conf_data, aes(x = reorder(conference, total_points), y = total_points)) +
  geom_col(fill = "#1e3a8a", width = 0.65) +
  geom_text(aes(label = paste0(total_points, " pts (", all_americans, " All-Americans)")),
            hjust = -0.05, size = 3.6, fontface = "bold", color = "#1e293b") +
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.28))) +
  labs(
    title = "National Championship Points by Conference",
    subtitle = "Total points scored and individual All-Americans (Top 8) produced at NAIA Nationals",
    x = NULL,
    y = "Total Points Scored"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.major.y = element_blank(),
    plot.title = element_text(face = "bold", color = "#0f172a"),
    plot.subtitle = element_text(color = "#64748b", margin = margin(b = 15)),
    axis.text.y = element_text(face = "bold", color = "#334155")
  )
```

## Detailed Conference Breakdown

The table below measures conference strength across five key dimensions: total national qualifiers, tournament team points, average points per wrestler, overall match win rate, All-Americans (Top 8 finishers), and National Champions.

```{r}
#| echo: false
#| message: false
#| warning: false

rows_html <- paste(
  sprintf(
    '<tr><td><strong>%s</strong></td><td>%s</td><td><span class="badge-weight">%s pts</span></td><td>%s</td><td>%s - %s</td><td><span class="badge-place">%s%%</span></td><td><span class="badge-gold">%s All-Americans</span></td><td><span class="badge-season">%s Champ%s</span></td></tr>',
    conf_data$conference,
    conf_data$qualifiers,
    conf_data$total_points,
    conf_data$avg_points,
    conf_data$wins,
    conf_data$losses,
    conf_data$win_pct,
    conf_data$all_americans,
    conf_data$champions,
    ifelse(conf_data$champions == 1, "", "s")
  ),
  collapse = ""
)

HTML(paste0(
  '<div class="table-wrapper">',
  '<table id="conferenceTable" class="table table-hover">',
  '<thead><tr><th>Conference</th><th>Qualifiers</th><th>Total Points</th><th>Avg Pts/Wrestler</th><th>Record (W-L)</th><th>Win %</th><th>All-Americans</th><th>Champions</th></tr></thead>',
  '<tbody>', rows_html, '</tbody>',
  '</table>',
  '</div>',
  '<script>',
  'function makeTableSortable(tableId) {',
  '  const table = document.getElementById(tableId);',
  '  if (!table) return;',
  '  const headers = table.querySelectorAll("thead th");',
  '  headers.forEach((th, colIdx) => {',
  '    th.style.cursor = "pointer";',
  '    th.title = "Click to sort";',
  '    th.setAttribute("data-title", th.textContent.trim());',
  '    th.textContent = th.getAttribute("data-title") + " ↕";',
  '    let asc = true;',
  '    th.addEventListener("click", () => {',
  '      const tbody = table.querySelector("tbody");',
  '      const rows = Array.from(tbody.querySelectorAll("tr"));',
  '      rows.sort((a, b) => {',
  '        const valA = a.children[colIdx].textContent.trim();',
  '        const valB = b.children[colIdx].textContent.trim();',
  '        const numA = parseFloat(valA);',
  '        const numB = parseFloat(valB);',
  '        if (!isNaN(numA) && !isNaN(numB)) {',
  '          return asc ? numA - numB : numB - numA;',
  '        }',
  '        return asc ? valA.localeCompare(valB) : valB.localeCompare(valA);',
  '      });',
  '      rows.forEach(r => tbody.appendChild(r));',
  '      headers.forEach(h => {',
  '        h.textContent = h.getAttribute("data-title") + " ↕";',
  '      });',
  '      th.textContent = th.getAttribute("data-title") + (asc ? " ▲" : " ▼");',
  '      asc = !asc;',
  '    });',
  '  });',
  '}',
  'makeTableSortable("conferenceTable");',
  '</script>'
))
```
